---
title: "README"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{README}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(FarsFinal)
```

---
title: "README.Rmd"
author: "Marc Eres"
date: "23/9/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# US FARS (Fatality Analysis Recording System)

This package sole objective is to produce graphics of the accidents in US.

## The `make_filename` function

This function generates a filename.

## The `fars_read` function

The `fars_read` will use as input the filename string from `make_filename`.

Based on the archives from US FARS that are located in the documents folder.

## The `fars_read_years` function

This functions uses both functions (`make_filename` and `fars_read`) to generate a list.

## The `fars_summarize_years` function

This functions print a summary.

## The `fars_map_state` function

Plot a Graphic of each State of US.

# Dependencies

* dplyr
* magrittr
* tidyr
* rlang
* graphics
* maps
